Who's Homeless in Toronto: Major Trends in Single Adults Aged 25 to 44 Becoming Homeless from 2018 to 2024

### 2024-09-27 paper/paper.qmd
style the paper and fix typo

In this report, @sec-data-tools describes the data tools I used to analyze the data, and @sec-data-source-and-measurement explains the context and measurements used with this dataset. @sec-data-selection explains the reasons for not choosing another database. @sec-Results presents and describes the demographic distribution and trends of homelessness in graphs and charts. @sec-Discussion analyzes the information in the graphs in the context of the community and describes the limitations of the study.

@@

# Discussion {#sec-data}

>>>>

In this report, @sec-data-tools describes the data tools I used to analyze the data, and @sec-data-source-and-measurement explains the context and measurements used with this dataset. @sec-data-selection explains the reasons for not choosing another database. @sec-result presents and describes the demographic distribution and trends of homelessness in graphs and charts. @sec-discussion analyzes the information in the graphs in the context of the community and describes the limitations of the study.

@@

# Discussion {#sec-discussion}
